Analysis of Security-Cost Trade-off of Fully Homomorphic Encryption Schemes

### 2013-06-10 Report/article.tex
l
Article changed
min max

\section{ Didactic example :  Maximum of two integer (1 page)}

\subsection{Input Program for Fully Homomorphic Encryption Scheme}

Details of the circuit or the program used to calculate the maximum of two bounded integers.

@@

Analyse the cost of the program wrt SV, BGV.

@@

Once for all analysis of common operations(KeyGen, Encrypt, Decrypt of 1 bit) varying the algorithmic and security parameters.

Measurements taken are CPU time, Wall Time, Memory Usage by varying the input size  and the algorithmic parameters. Noise reduction threshold.

\paragraph{KeyGen}

\paragraph{Encryption and Decryption}

\section{Choice of Benchmarks}

@@

\section{Analysis of the results}

>>>>

\section{ Didactic example :  Min-Max (1 page)}
Min-Max of sequence of n-btis with arithmetic operations and without branching.
\subsection{Input Program for Fully Homomorphic Encryption Scheme}

 \caption{Min-Max\label{Code:algo}}

@@

The cost \texttt{aIsGreater} is:\\
 $2*encrypt+n*(3*encrypt+7*add+7*mul)$ .\\
The cost of this algorithm \texttt{min\_max} is:\\
$ encrypt+aIsGreater+2*n*(encrypt+3add+3mull)$\\
Thus this algorithm has $\theta(n)$ complexity.

@@

Measurements taken are CPU time, Wall Time, Memory Usage by varying the input size  and the algorithmic parameters. Noise reduction threshold.\\
Here we estimate the performance of this program in terms of run time for KeyGen, Encrypt, Decrypt and the Min-Max algorithm.
\begin{itemize}

\item KeyGen\\
The measured time execution for KeyGen($N, \mu$)  for fixed values of parameters: $N=8$ and $\mu = 4$ shows a variation from 0.31 s to 13.41 s with mean = 2.726 s.\\
\item {Encryption and Decryption}\\

\item {Cost time of Min-Max program}\\
\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
  \hline
  nbits  & 3 & 4 & 5 & 6 & 7 & 8 &  9  & 10 \\
  \hline
  time(s) & 4.17 & 5.84 & 7.18 & 4.29 & 4.65 & 5.9 & 6.71 & 6.73\\
  \hline
\end{tabular}
\end{itemize}
\section{Choice of Benchmarks}

@@

\section{Evaluation on the benchmarks}
Measurements by varying the parameters or the plaintext size.
\section{Analysis of the results}
